\chapter{Conclusions and Future Work}
\label{chap:conclusions}
\lhead{\emph{Conclusions}}

\section{Discussion}
This research phase of the NoteReader project has been instrumental in identifying and understanding the critical challenges and opportunities in integrating document reading and note-taking. The work focused on analyzing existing solutions, exploring technical frameworks, and conceptualizing a solution that addresses the gaps in current tools.

\subsection{Key Considerations}
\begin{itemize}
    \item \textbf{Fragmented Existing Solutions:} Existing tools often focus on either document reading or note-taking, creating a gap in unified functionality.
    \item \textbf{Technical Feasibility:} Ensuring multiplatform compatibility, especially with varying operating systems, was identified as a core challenge for future implementation.
    \item \textbf{User Experience Design:} Balancing functionality with simplicity highlighted the need for iterative user feedback to ensure an intuitive interface.
    \item \textbf{Data Synchronization Concerns:} Utilizing version control systems like Git
\end{itemize}



\section{Conclusion}
The research conducted during this phase underlines the need for a unified application that seamlessly integrates document reading and note-taking. The primary insights include:

\begin{enumerate}
    \item \textbf{Clear Market Gap:} There is a significant gap in the market for tools that prioritize both document reading and note-taking equally.
    \item \textbf{Technological Opportunities:} Technologies like Kotlin Multiplatform and Markdown support offer viable paths to create a flexible and scalable application.
\end{enumerate}

\section{Future Work}
The next steps involve transitioning from the research phase to implementation, focusing on the following areas:

\subsection{Prototype Development}
\begin{itemize}
    \item Build a functional prototype focusing on core features such as document rendering and contextual note-taking.
    \item Test the prototype for usability and cross-platform functionality.
\end{itemize}

\subsection{Technical Enhancements}
\begin{itemize}
    \item Explore and integrate frameworks like PDF.js and Tesseract for document rendering and OCR capabilities.
\end{itemize}

\subsection{User Feedback}
\begin{itemize}
    \item Conduct user surveys and usability tests to gather insights on interface design and feature prioritization.
    \item Refine the design based on iterative feedback.
\end{itemize}

\subsection{Advanced Features (Stretch Goals)}
\begin{itemize}
    \item Investigate the feasibility of integrating handwriting recognition and voice-to-text dictation.
\end{itemize}

