% The Thesis Abstract is written here (and kept just one page long or less). The page is kept centered vertically so can expand into the blank space above the title too\ldots Briefly, write in 3-4 paragraphs on what your project is about. This is a more precise version of your project abstract submitted on week 1 updated with developments between then and the submission time. Try to include the main features and functional requirements provided. As the title suggests this section is normally the only thing an executive would read so it MUST get across the main elements of the project.

When revising a topic, the first approach is usually to review the notes you took when studying the material. These notes are often shorthand and are usually incomplete. As a result it is important to reference back to the original material for full understanding. 
	
Managing storage of documents alongside digital note taking causes friction in the learning process, and without good self imposed organization it is easy to lose reference material. 

The purpose of this project is to create a suite of applications which assist in cataloging digital notes alongside study material. 

There are a large number of existing note taking solutions. None however treat document reading as a first class priority. Likewise there are a large number of document readers available, however none treat note taking as a first class priority. 

Current solutions (such as Microsoft OneNote) require large file sizes, synced between devices using expensive cloud storage providers, often requiring costly monthly subscriptions.